Reply to: 2022-05603 Intentional release of native species undermines ecological stability

### 2022-10-20 rmd/manuscript.Rmd
rmd

```{r figure-layout, fig.cap= paste0("Theory and empirical observations agree that intentional release destabilizes community dynamics. In A and B, panels and colors distinguish response variables and species groups. (A) Theoretical predictions. Dots represent individual simulation replicates, and lines are the loess curves fitted to simulated data with their 95% confidence (dark shade) and 50% prediction intervals (light shade). Parameters used in this simulation are: intrinsic growth rate of an enhanced species $r_1=$ ", round(na.omit(unique(df_sim$r1)), 2), ", average interspecific competition $\\bar{\\alpha}=$ ", round(na.omit(unique(df_sim$alpha)), 2), ", carrying capacity $K=$ ", round(na.omit(unique(df_sim$k)), 2), ", environmental stochasticity $\\sigma_{\\epsilon}=$ ", round(na.omit(unique(df_sim$sd_env)), 2), ", relative fitness of captive-bred individuals $f_R=$ ", round(na.omit(unique(df_sim$phi)), 2), ". These parameter values are comparable to the estimates of the multi-species Ricker model. (B) Empirical evidence. Dots represent observations at 97 sites within 31 watersheds. Lines and shades are the predicted values and their 95% credible intervals of the regression models, and line types correspond to the coefficient's posterior probabilities. Effective release is a latent explanatory variable estimated in our hierarchical Baysian model. See Methods for details. Full statistics were reported in Tables S6-8. (C) Map of sampling sites (black dots) in Hokkaido, Japan. (D) Example of a protected watershed (Okushibetsu). (E) Masu salmon *Oncorhynchus masou*. Photo credit: Akira Terui")}

@@

The reduced fitness of hatchery masu salmon may also play a role in the observed response. Like other salmonids, masu salmon exhibits a life history of "partial migration"; in our study region, the majority of individuals migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @sahashiMigrationCostsDrive2013; @moritaTemperaturedependentVariationAlternative2014]. It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress], and such genetic effects may accumulate as the number of generations in captivity increases [@arakiGeneticEffectsCaptive2007]. Typically, hatchery masu salmon are reared in captivity for two to four generations. Thus, the fitness decline may be substantial. In addition, the aggressive behavior of hatchery salmons may make them vulnerable to predation [@weberInteractionsHatcheryWild2003]. The multiple fitness disadvantages may add to negative density dependence to influence community stability.

@@

```{r figure-alpha, fig.cap="Estimated competition coefficients of the multi-species Ricker model. Dots represent a given pair of taxa, and box plots show median (vertical center line) and quartiles (box limits) with whiskers extending up to the most extreme data points that are within ±1.5 interquartile range. The density plot on the top shows the overall distribution of the competition coefficient. Colors distinguish taxa. The vertical broken line denotes the overall median value."}

>>>>

```{r figure-layout, fig.cap= paste0("Theory and empirical observations agree that intentional release destabilizes community dynamics. In A and B, panels and colors distinguish response variables and species groups. (A) Theoretical predictions. Dots represent individual simulation replicates, and lines are the loess curves fitted to simulated data with their 95% confidence (dark shade) and prediction intervals (light shade). Parameters used in this simulation are: intrinsic growth rate of an enhanced species $r_1=$ ", round(na.omit(unique(df_sim$r1)), 2), ", average interspecific competition $\\bar{\\alpha}=$ ", round(na.omit(unique(df_sim$alpha)), 2), ", carrying capacity $K=$ ", round(na.omit(unique(df_sim$k)), 2), ", environmental stochasticity $\\sigma_{\\varepsilon}=$ ", round(na.omit(unique(df_sim$sd_env)), 2), ", relative fitness of captive-bred individuals $f_R=$ ", round(na.omit(unique(df_sim$phi)), 2), ". These parameter values are comparable to those estimated in the empirical Ricker model. (B) Empirical evidence. Dots represent observations at 97 sites within 31 watersheds. Lines and shades are the predicted values and their 95% credible intervals of the regression models, and line types correspond to the coefficient's posterior probabilities. Effective release is a latent explanatory variable estimated in our hierarchical Baysian model. See Methods for details. Full statistics were reported in Tables S6-8. (C) Map of sampling sites (black dots) in Hokkaido, Japan. (D) Example of a protected watershed (Okushibetsu). (E) Masu salmon *Oncorhynchus masou*. Photo credit: Akira Terui")}

@@

The reduced fitness of hatchery masu salmon may also play a role in the observed response. Like other salmonids, masu salmon exhibits a life history of "partial migration"; in our study region, the majority of individuals migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @sahashiMigrationCostsDrive2013; @moritaTemperaturedependentVariationAlternative2014]. It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress], and such genetic effects may accumulate as the number of generations in captivity increases [@arakiGeneticEffectsCaptive2007]. Typically, hatchery masu salmon are reared in captivity for two to four generations. Given the duration of the extensive release program (\> 60 years), it is conceivable that the "hatchery gene" has spread within the wild populations with measurable fitness declines. This effect may add to negative density dependence to influence community stability.

@@

```{r figure-alpha, fig.cap="Estimated competition coefficients of the multi-species Ricker model. Dots represent a given pair of taxa, and box plots show median (vertical center line) and quartiles (box limits) with whiskers extending up to the most extreme data points that are within $\\pm 1.5$ interquartile range. The density plot on the top shows the overall distribution of the competition coefficient. Colors distinguish taxa. The vertical broken line denotes the overall median value."}

### 2022-10-20 rmd/reply_r1.Rmd
rmd

Dear Editor,

Thank you for giving us the opportunity to revise our manuscript. The comments were very helpful to improve our manuscript. When revising the manuscript, we have put a particular emphasis on the following points:

1.  **Improve the introduction and implications**: both reviewers noted an absence of context in the previous manuscript. We agree with this comment. To address this issue, we revised the text to better contextualize our work. In particular, we have carefully reviewed cases to which our findings may apply, and discussed the relevance of our work to those systems.
2.  **Two-species simulation.** The Editor suggested to include a two-species simulation to guide the full community model. We really appreciate this suggestion and were able to draw deeper insights into our theoretical analysis. This improvement helped address the concern raised by the reviewer 2 (they pointed the lack of depth in theoretical analysis). We revised Methods and Results in accordance with this change. In particular, we removed the old sensitivity analysis as it was redundant with two-species simulations.
3.  **Ecological interpretation of our empirical results (i.e., masu salmon system).** The reviewers and editor pointed that the interpretation of our empirical analysis is superficial -- we agree with this comment too. We have carefully enriched the text related to this issue. We have greatly increased the number of citations and discussed more carefully possible mechanisms that may produce the observed patterns. In particular, we have added a new Ricker model analysis for empirical data to estimate competition coefficients in stream fish communities. The estimated parameter indicated that competition among species certainly exists.
4.  **Life history of masu salmon.** Lastly, we enriched the text for life history of masu salmon and how release programs for this species are operated.

@@

Akira Terui on behalf of the authors

@@

*Because the Ricker model can yield damped oscillations, limit cycles, and even chaos depending on intrinsic growth rate, I would have first understood the impact of population supplementation analytically in a deterministic two species system. This is straightforward and relevant since the tendency to experience fluctuations without stochasticity is the baseline for your model. Moreover, this analysis can illuminate how you organize any exploration of parameter space. In particular, I would vary intrinsic rate of increase so that it captured monotonic convergence to equilibrium, damped oscillations en route to equilibrium, limit cycle, and chaos....The results reported from the model lack depth - especially considering the many possible parameter combinations. Since the Ricker model can produce fluctuations deterministically, the tendency to fluctuate deterministically (which is governed by intrinsic rate of increase) should be used to organize the simulation results. A more systematic examination of results would cross varying levels of K with varying r's, where the r's selected capture the different dynamical possibilities of the deterministic model.*

> Thank you for this constructive comment! We followed this direction, analyzing the model in a two-species community to guide a whole community analysis. As we detailed in the maintext, the different combinations of $r$ and $K$ produced distinct parameter spaces where intentional release had destabilizing, neutral, and stabilizing effects. Stabilizing effects appeared when the community shows limit cycles or chaos; otherwise, intentional release had destabilizing effects in general. We have clarified this point in the revised manuscript (see section **Theoretical prediction**).

@@

> XXX

*Obviously species do not go extinct in your simulations (since populations can never go to zero or become negative). You contrive extinction to be an N = .01 or lower. In your words "the number of species persist (defied as 𝑁𝑖 \> 0.01 at 𝑡 = 1600)". Apart from the typo it is not clear to me if you:\
\
1) at t= 1600, you simply tally up all N's less than .01 and call that an extinction. or, alternatively,\
\
2) whenever a species' population falls below .01 during the course of the potential 1600 time steps, that species is considered extinct. So if at time step 634, N fell to .005, that would then be an absorbing boundary and the species is removed from the simulation.\
\
It is essential that you make clear whether it is #1 or #2 above that accounts for the loss of species.*

> XXX

*Both reviewers noted an absence of context, and literature cited that might better provide a framework for this study. What other species might this apply to? What are levels of supplementation in other salmon systems? The discussion does not place the work in the context of general research regarding captive breeding for enhancement, salmon hatcheries, and salmon conservation.*

> XXX

*The discussion of the masu data is too superficial. You need to include more about their life history and the supplementation systems. To what extent do the released salmon overlap with other species in space and time?*

> XXX

@@

> XXX

@@

> XXX

@@

> XXX

@@

> Masu salmon spend at least one year before sea migration (they show partial migration, and some males stay in freshwater for their entire life). We have clarified details of masu salmon's life history.

@@

> Thank you - we have given a deep thought on this. Masu salmon has a 1-year marine life stage. However, many other species are also diadromous, and some of them return freshwater in a couple of months (e.g., amphidromous). Given the complexity of this system, we reconsidered our state-space model to account for up to AR3 process (fish species in our system typically 1-3 years of life-span; see Methods for the revised model). The results were qualitatively similar.

@@

> XXX

@@

> We have detailed species information in Table S2. Masu salmon often co-occur with white-spotted charr, sculpins, and stone loaches. Since our watersheds are "protected" watersheds, any form of exploitation (including angling) is not allowed (regardless of fish species). Therefore, other factors are very unlikely to shape the observed patterns of temporal community variability. Please note that we have statistically accounted for natural variation in land use, watershed size, climate etc.

@@

*The general model seems logical in that there is a non-linear response to numbers of releases. It does not seem too surprising that when releases are 5x carrying capacity that there is a negative impact, especially given a fairly large alpha.*

> We agree that our results are not surprising -- we are not surprised either. However, we strongly believe that our result is important and worth publishing because to our knowledge, no study has rigorously quantified the community-level impact of intentional release in the long-term. Also, and perhaps more importantly, many release programs for commercial and recreational species release **millions of individuals to a single system every year** (clarified in the revised manuscript)! This magnitude is way larger than the release program in our study system. Therefore, release numbers of $5\times$ carrying capacity seem even conservative to us. Although we cannot provide quantitative evidence for this claim (we found no data on the carrying capacities of the recipient ecosystems), our analysis should represent a conservative scenario, rather than an unrealistic extreme scenario.
>
> Regarding the competition coefficient, please find that the interspecific competition coefficients $\alpha_{ij}$ ($i \ne j$) are measured relative to intraspecific competition -- i.e., two competing species can coexist when $\alpha_{ij} < 1$ (if carrying capacities are identical between the species). The values in our simulation (0.25 or 0.50 in the revised manuscript) are thus weak enough to allow species co-existence in the absence of intentional release. Therefore, it is certain that the intentional release disrupted the sensitive balance of species interactions. In the revised text, we have also provided empirical estimates of species interactions -- the median value was 0.29, so our simulation setup is reasonable.

*...in the mean* $\mu$ *panel in Figure 1A, the enhanced population shows no effect of releases until about 2x carrying capacity, which seems significant. This appears to occur at the same time there is steep decline of the unenhanced species, even when the number of releases is below.*

> Thank you for this comment. We agree that this pattern is important, and we do acknowledge that there are cases where intentional release works very well (see the revised text; last paragraph of **Theoretical prediction**). However, our focus here is not the influence of intentional release on the enhanced species -- we are interested in how unenhanced species respond to the intentional release. This is the knowledge gap we are trying to fill, as no study has focused on this "side-effect" of intentional release so far. We hope the reviewer will understand the significance of this finding.

@@

> Thank you for this critical comment. Following the editor's suggestion, we have greatly improved the analysis by introducing two-species simulations (see our response to editor).

@@

> Thank you, we agree that a detailed life-history model will provide useful insights into salmon management. However, we decided not to perform this analysis for the following reasons. First, given the readership of PNAS, as well as the suggestions from reviewer 1 and editor, we believe it is important to keep our model as general as possible. In fact, as clarified in the revised manuscript, there are a number of cases where our phenomenological model may apply. Second, a detailed life-history model has already been developed by Morita et al. [@moritaTemperaturedependentVariationAlternative2014]. The readers interested in specifics of masu salmon can refer to this article. We have cited it in the revised manuscript. Lastly, we believe the reviewer misread our results in the previous manuscript. Table S9 in the previous manuscript did not show significant effects of ocean productivity (coef = $0.09 \pm 0.29$) or forest cover (coef = $0.36 \pm 0.28$), thus largely overlapping zero or marginal at best. This result remains the same in the improved analysis in the revised manuscript. Therefore, there is little evidence supporting the importance of detailed life-history processes in explaining long-term population dynamics for our dataset.

@@

> We are glad that the reviewer caught this issue. We improved as follows:
>
> \- Enriched the text explaining masu salmon's life history; they spend at least one year in freshwater.
>
> \- Added species traits to Table S2.
>
> \- Added spatial/temporal overlap between masu salmon and other species (see Table S16 for co-occurrence matrix).
>
> As we clarified in the revised text, we are pretty sure that (hatchery) masu salmon interact with other species. Indeed, masu salmon always occurred with other species (in particular, white-spotted charr, sculpins, stone loaches). In addition, there are numerous research documenting competition between masu salmon and other stream fish species. We have clarified these points in the revised manuscript.

@@

> Thank you, this is very important. To address this issue, we have developed a Bayesian Ricker model to estimate competition coefficients in our data (note: we used a subset of data because it requires non-sparse data to estimate parameters reliably). The results were very promising, supporting the considerable interspecific competition among stream fishes. We chose this approach to make it directly comparable with theoretical parameters. As the reviewer suggests, spatial/diet overlap may be useful, but it does not necessarily translate into "population" level interactions (in fact, estimated competition coefficients varied greatly among sites for a given species pair). Therefore, our approach would give stronger evidence for interspecific competition occurring in natural systems.

*The Introduction of the paper does not set up the problem well. There is a large literature about captive breeding for enhancement, and an especially large literature for salmonids. For example, the paper suggests in line 45 that "use of captive breeding is perhaps because of the myth that the demographic benefits of released individuals may exceed the associated risks." This statement highlights that the introduction is not well grounded in the vast literature regarding the science and politics of hatcheries. Similarly, the discussion of the paper does not place this work in the larger body of scholarship around captive breeding for enhancement , salmon hatcheries, and salmon conservation.*

> We appreciate the careful reading by the reviewer. We agree, and we have substantially improved the introduction and discussion to address this issue. Specifically, we now recognized that there are a number of cases where stock enhancement is economically successful -- we have mentioned these examples to properly develop a context. Also, where applicable, we have softened the language throughout the manuscript. If there are information/issues that we have missed, please let us know and we will address them too. This insightful comment helped a lot to avoid delivering wrong messages.

>>>>

Dear editor,

Thank you for allowing us to revise our manuscript. The comments were very helpful in improving our manuscript. When revising the manuscript, we have put a particular emphasis on the following points:

1.  **Improve the introduction and implications**: both reviewers noted an absence of context in the previous manuscript. We agree with this comment. We revised the text to contextualize our work better to address this issue. In particular, we have carefully reviewed cases to which our findings may apply and discussed the relevance of our work to those systems.
2.  **Two-species simulation.** The Editor suggested including a two-species simulation to guide the full community model. We appreciated this suggestion and were able to draw deeper insights into our theoretical analysis. This improvement helped address the concern raised by reviewer 2 (they pointed out the lack of depth in theoretical analysis). We revised the Methods and Results following this change. In particular, we removed the old sensitivity analysis as it was redundant with two-species simulations.
3.  **Ecological interpretation of our empirical results (i.e., masu salmon system).** The reviewers and editor pointed out that the interpretation of our empirical analysis is superficial -- we agree with this comment too. We have carefully enriched the text related to this issue. We have greatly increased the number of citations and discussed possible mechanisms that may produce the observed patterns more carefully. In particular, we have added a new Ricker model analysis for empirical data to estimate competition coefficients in stream fish communities. The estimated parameter indicated that competition among species certainly exists.
4.  **Life history of masu salmon.** Lastly, we enriched the text for the life history of masu salmon and how release programs for this species are operated.

@@

Akira Terui, on behalf of the authors

@@

*Because the Ricker model can yield damped oscillations, limit cycles, and even chaos depending on the intrinsic growth rate, I would have first understood the impact of population supplementation analytically in a deterministic two species system. This is straightforward and relevant since the tendency to experience fluctuations without stochasticity is the baseline for your model. Moreover, this analysis can illuminate how you organize any exploration of parameter space. In particular, I would vary the intrinsic rate of increase so that it captured monotonic convergence to equilibrium, damped oscillations en route to equilibrium, limit cycle, and chaos....The results reported from the model lack depth - especially considering the many possible parameter combinations. Since the Ricker model can produce fluctuations deterministically, the tendency to fluctuate deterministically (which is governed by intrinsic rate of increase) should be used to organize the simulation results. A more systematic examination of results would cross varying levels of K with varying r's, where the r's selected capture the different dynamical possibilities of the deterministic model.*

> Thank you for this constructive comment! We followed this direction, analyzing the model in a two-species community to guide a whole community analysis. As we detailed in the main text, the different combinations of $r$ and $K$ produced distinct parameter spaces where intentional release had destabilizing, neutral, and stabilizing effects. Stabilizing effects appeared when the community showed limit cycles or chaos; otherwise, the intentional release had destabilizing effects in general. We have clarified this point in the revised manuscript (see section **Theoretical prediction**).

@@

> We have now used relevant values in the simulation. Myer et al @myersMaximumReproductiveRate1999 has provided a comprehensive list of ricker model parameters, so we referenced this work. Specifically, r = 1.5 seems a reasonable proxy for masu salmon and other salmonid species. Also, we changed the value of competition to make it comparable to our estimates of $\alpha_{ij}$ ($\approx 0.25$). The value of $\sigma_{\varepsilon}$ in the original analysis was also comparable.

*Obviously species do not go extinct in your simulations (since populations can never go to zero or become negative). You contrive extinction to be an N = .01 or lower. In your words "the number of species persist (defined as N \> 0.01 at t = 1600)". Apart from the typo it is not clear to me if you:\
\
1) at t= 1600, you simply tally up all N's less than .01 and call that an extinction. or, alternatively,\
\
2) whenever a species' population falls below .01 during the course of the potential 1600 time steps, that species is considered extinct. So if at time step 634, N fell to .005, that would then be an absorbing boundary and the species is removed from the simulation. It is essential that you make clear whether it is #1 or #2 above that accounts for the loss of species.*

> Although we used #1 in the previous version, we thought this was not the best - in the revised manuscript, we used #2. We clarified this point in the revised Methods.

*Both reviewers noted an absence of context and literature cited that might better provide a framework for this study. What other species might this apply to? What are levels of supplementation in other salmon systems? The Discussion does not place the work in the context of general research regarding captive breeding for enhancement, salmon hatcheries, and salmon conservation.*

> Agreed. We have greatly improved the introduction and Discussion (paragraph L184 --, paragraph L208 --). We have clarified that our findings seem quite general for two reasons. (1) the scale of other release programs (mussels, crustaceans, birds, insects, and other fish) is generally way larger than our release program. For example, the largest release program for pink salmon in Alaska releases \> 600 million fish year^-1^ (note: our program releases only 0.24 million fish per year at the most intense site). (2) Most release programs aim to help declining populations in degraded habitats. In these habitats, the carrying capacities are likely compromised - a theoretical premise for the destabilizing effect to emerge.

*The Discussion of the masu data is too superficial. You need to include more about their life history and the supplementation systems. To what extent do the released salmon overlap with other species in space and time?*

> We have addressed the concerns raised by the reviewers. Please see our response to specific comments. Also, we have improved our regression analysis to account for the spatial overlap of hatchery salmon and other wild fishes. Since we do not have exact information on where hatchery fish are released (we have partial information -- updated our map to include this information; see Figure 1C), we performed the *post hoc* estimation of spatial overlap within the regression model (see Methods, "effective release"). We believe this will increase the validity of our results as it enabled us to use 97 site replicates fully to estimate the effect of releases.

@@

> We have rephrased.

@@

> Thank you for the great comment! As you can see in our response to the editor's comment, we have greatly improved the introduction and Discussion (paragraph L208 --). We believe our findings are broadly applicable across taxa and ecosystems.

@@

> This greatly helped improve our manuscript, making the results relevant to other systems. We included more information on other salmon and fishery release programs (paragraph L184 --).

@@

> Masu salmon spend at least one year before sea migration (they show partial migration, and some males stay in freshwater for their entire life). We have clarified the details of masu salmon's life history.

@@

> Thank you - we have given deep thought to this. Masu salmon has a 1-year marine life stage. However, many other species are also diadromous; some return freshwater in a couple of months (e.g., amphidromous). Given the complexity of this system, we reconsidered our state-space model to account for up to the AR3 process (fish species in our system typically have 1-3 years of lifespan; see Methods for the revised model). The results were qualitatively similar.

@@

> Good point -- unfortunately, we do not have any data to show quantitative patterns. The "hatchery" gene has likely spread within the wild populations, given the duration of the extensive release programs. We have briefly mentioned this in the revised text (paragraph L169 --).

@@

> We have detailed species information in Table S2. Masu salmon often co-occur with white-spotted charr, sculpins, and stone loaches. Since our watersheds are "protected" watersheds, any form of exploitation (including angling) is not allowed (regardless of fish species). Therefore, other factors are unlikely to shape the observed patterns of temporal community variability. Please note that we have statistically accounted for natural variations in land use, watershed size, climate etc.

@@

*The general model seems logical in that there is a non-linear response to the number of releases. It does not seem too surprising that when releases are 5x carrying capacity that there is a negative impact, especially given a fairly large alpha.*

> We agree that our results are not surprising -- we are not surprised either. However, we strongly believe that our result is important and worth publishing because, to our knowledge, no study has rigorously quantified the community-level impact of intentional release in the long term. Also, perhaps more importantly, many release programs for commercial and recreational species release **millions of individuals to a single system every year** (clarified in the revised manuscript)! This magnitude is way larger than the release program in our study system. Therefore, release numbers of $5\times$ carrying capacity seem conservative to us. Although we cannot provide quantitative evidence for this claim (we found no data on the carrying capacities of the recipient ecosystems), our analysis should represent a conservative rather than an unrealistic extreme scenario.
>
> Regarding the competition coefficient, please find that the interspecific competition coefficients $\alpha_{ij}$ ($i \ne j$) are measured relative to intraspecific competition -- i.e., two competing species can coexist when $\alpha_{ij} < 1$ (if carrying capacities are identical between the species). The values in our simulation (0.25 or 0.50 in the revised manuscript) are thus weak enough to allow species co-existence without intentional release. Therefore, it is certain that the intentional release disrupted the sensitive balance of species interactions. In the revised text, we have also provided empirical estimates of species interactions -- the median value was 0.29, so our simulation setup is reasonable.

*...in the mean* $\mu$ *panel in Figure 1A, the enhanced population shows no effect of releases until about 2x carrying capacity, which seems significant. This appears to occur at the same time there is a steep decline of the unenhanced species, even when the number of releases is below.*

> Thank you for this comment. We agree that this pattern is important, and we acknowledge that there are cases where intentional release works very well (see the revised text; last paragraph of **Theoretical prediction**). However, our focus here is not the influence of intentional release on the enhanced species -- we are interested in how unenhanced species respond to the intentional release. This is the knowledge gap we are trying to fill, as no study has focused on this "side-effect" of intentional release. We hope the reviewer will understand the significance of this finding.

@@

> Thank you for this critical comment. Following the editor's suggestion, we have greatly improved the analysis by introducing two-species simulations (see our response to the editor).

@@

> Thank you, we agree that a detailed life-history model will provide useful insights into salmon management. However, we decided not to perform this analysis for the following reasons. First, given the readership of PNAS and the suggestions from reviewer 1 and the editor, we believe it is important to keep our model as general as possible. In fact, as clarified in the revised manuscript, there are many cases where our phenomenological model may apply. Second, Morita et al. have already developed a detailed life-history model [@moritaTemperaturedependentVariationAlternative2014]. Readers interested in the specifics of masu salmon can refer to this article. We have cited it in the revised manuscript. Lastly, we believe the reviewer misread our results in the previous manuscript. Table S9 in the previous manuscript did not show significant effects of ocean productivity (coef = $0.09 \pm 0.29$) or forest cover (coef = $0.36 \pm 0.28$), thus largely overlapping zero or marginal at best. This result remains the same in the improved analysis in the revised manuscript. Therefore, there is little evidence supporting the importance of detailed life-history processes in explaining long-term population dynamics for our dataset.

@@

> We are glad that the reviewer caught this issue. We improved as follows:
>
> \- Enriched the text explaining masu salmon's life history; they spend at least one year in freshwater.
>
> \- Added species traits to Table S2.
>
> \- Added spatial/temporal overlap between masu salmon and other species (see Table S16 for co-occurrence matrix).
>
> As we clarified in the revised text, we are pretty sure that (hatchery) masu salmon interact with other species. Indeed, masu salmon always occurred with other species (in particular, white-spotted charr, sculpins, stone loaches). In addition, numerous research documents competition between masu salmon and other stream fish species. We have clarified these points in the revised manuscript.

@@

> Thank you, this is very important. To address this issue, we have developed a Bayesian Ricker model to estimate competition coefficients in our data (note: we used a subset of data because it requires non-sparse data to estimate parameters reliably). The results were very promising, supporting the considerable interspecific competition among stream fishes. We chose this approach to make it directly comparable with theoretical parameters. As the reviewer suggests, spatial/diet overlap may be useful. However, it does not necessarily translate into "population" level interactions (estimated competition coefficients varied greatly among sites for a given species pair). Therefore, our approach would give stronger evidence for interspecific competition occurring in natural systems.

*The Introduction of the paper does not set up the problem well. There is a large literature about captive breeding for enhancement and an especially large literature for salmonids. For example, the paper suggests in line 45 that the "use of captive breeding is perhaps because of the myth that the demographic benefits of released individuals may exceed the associated risks." This statement highlights that the introduction is not well grounded in the vast literature regarding the science and politics of hatcheries. Similarly, the Discussion of the paper does not place this work in the larger body of scholarship around captive breeding for enhancement, salmon hatcheries, and salmon conservation.*

> We appreciate the careful reading by the reviewer. This insightful comment helped a lot to avoid delivering the wrong messages. We agree and have substantially improved the introduction and Discussion to address this issue. Specifically, we now recognize that there are many cases where stock enhancement is economically successful -- we have mentioned these examples to develop a context properly. Also, where applicable, we have softened the language throughout the manuscript. If there are information/issues that we have missed, please let us know, and we will address them too.
